\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-08 paper.tex
Added a tentative conclusion

>>>>

\section{Conclusion}

This article does not claim to provide an exhaustive assessment of the
strengths and weaknesses of explicit knowledge management in a large robotic
architecture. Most of the ``lessons'' that we have ``learned'' are not new, and
the various scientific communities (task planning, architecture control, NLP,
geometric reasoning, social psychology...) that are related to human-robot
interaction and robotic cognition already know them.

One of the difficult challenge of cognitive robotics, however, is to overcome
the relative isolation of each of these communities, to build an embodied
agent, able to autonomously interact.

In this respect, our main contribution is to propose a critical look at a
viable robotic architecture that covers many of the facets of cognitive
robotics and that is actually deployed on several robots.

And if we had a single ``lesson'' to retain, it would likely be that one:
shifting from a robotic system design based on \emph{modules and APIs} to a
system based on \emph{modules and human-level semantic interfaces} has been the
main facilitator both for glueing together deliberative heterogeneous modules
in a meaningful way, and quickly developing new upper-cognition abilities,
including natural dialogue and theory of mind.
